Refractory anaphylaxis: Data from the European Anaphylaxis Registry

### 2018-11-21 analysis/paper/paper.Rmd
hotfix tables

```{r elicitorTab}
knitr::kable(elicitorTab[,c(0,1,5,6,7,8,2,3,4)+1], caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, Age is represented as a mean, p-value derived from the Fisher's exact test."
             #col.names = c("n","Age","Male sex [%]","Perioperative [%]","Food allergy [%]","refractory ANA [%]","severe ANA [%]","p value")

            #digits = 1,
             # align = rep("r",10),
             # trim=T,
             # scientific=F,
             # nsmall=3,
             #drop0trailing = F
             )
```

@@

knitr::kable(data.frame(c("Antibiotics","X-ray medium","Muscle relaxant","Legumes","Bee venom","Yellow-jacket venom"),
                   as.numeric(elicitExact[,2:4]) %>% matrix(nrow = 6)), 
             caption = "Summary of the elicitors broken down into specific elicitors from each group in the refractory anaphylaxis cases and severe anaphylaxis cases as a control. ANA - anaphylaxis, p-value derived from the Fisher's exact test. ",
             col.names = c("Elicitor","severe ANA [%]","refractory ANA [%]","p value"),
             digits = c(0,2,2,4)
             )
```

>>>>

```{r elicitorTab}
knitr::kable(elicitorTab[,c(0,1,5,6,7,8,2,3,4)+1], caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, Age is represented as a mean, p-value derived from the Fisher's exact test.",
             #col.names = c("n","Age","Male sex [%]","Perioperative [%]","Food allergy [%]","refractory ANA [%]","severe ANA [%]","p value")
              align = rep("r",10),
             nsmall=2)
            #digits = 1,
             # align = rep("r",10),
             # trim=T,
             # scientific=F,
             # nsmall=3,
             #drop0trailing = F

@@

knitr::kable(data.frame(c("Antibiotics","X-ray medium","Muscle relaxant","Legumes","Bee venom","Yellow-jacket venom"),
                   as.numeric(elicitExact[,2:4]) %>% matrix(nrow = 6)), 
             caption = "Summary of the elicitors broken down into specific elicitors from each group in the refractory anaphylaxis cases and severe anaphylaxis cases as a control. ANA - anaphylaxis, p-value derived from the Fisher's exact test. ",
             col.names = c("Elicitor","severe ANA [%]","refractory ANA [%]","p value")
             #digits = c(0,2,2,4)
             )
```
